\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\author{Ilya Skurikhin}
\title{75 Karma Rules}

\begin{document}

We thank you for using the Karma Platform. By using these products and services ("Services"), you are agreeing to these terms. Please read them carefully.

\section{Definitions}

\paragraph{Language}

This agreement was written in English (US). To the extent any translated version of this agreement conflicts with the English version, the English version controls.

\paragraph{Residence}

The living community ("colocation") situated at 75, Rue de Genève, 1004 Lausanne Switzerland.

\paragraph{75er}

A person who is living in the Residence, and who's lease is substantiated by a current and valid lease agreement ("bail à loyer").

\paragraph{We}

(us, our) are the developers of the Karma Platform. 

\paragraph{You}

(your) are the user of the Karma Platform ("KP"); delegates will be considered users if exercising a power of attorney on the behalf of a 75er.
	
\paragraph{Karma}

are points that can be received and transferred by You. The official abbreviation of the Karma is "K".

\paragraph{Karma Platform}

is the web interface through which users may make transfers of points and consult their balance. 

\section{Privacy}

Your privacy is very important to us. 

\section{Using our Services}

Don't misuse our Services. \\

Please follow the terms and use Services in the way that as we describe them in the interface and instructions we provide. You may use our Services only as permitted by law. We may stop providing our Services to you if you do not comply with our terms, or if we are suspecting misconduct.\\

Using Our Services does not give You ownership of any of the intellectual property rights in Our Services or the content You access. You may not use content from Our Services unless You obtain prior permission from its owner. \\

In connection with Your use of Our Services, we may send You service announcements, administrative messages, and other information. \\

Some of Our Services are available on mobile devices. Do not use these Services in a way that will divert Your attention while driving, or prevents You from obeying traffic laws.

\section{Your Account}

In order to use the Karma Platform, You will need an account. An account will be assigned to You by an administrator when you move in to the Residence. \\

To protect Your account, keep Your password confidential. You are responsible for the activity that happens on or through Your account.

\section{Karma Balance}

\begin{enumerate}
	\item When a 75er begins their lease, they can receive one Karma Balance.
	\item All new Karma Balances will contain 100 K.

\end{enumerate}

\section{Sending Karma}

\begin{enumerate}
	\item You may transfer all or part of the Karma in your Karma Balance to the Karma Balance of another 75er. 
	\item Transactions may mention a comment describing the motive of the transaction.
	\item Transactions are made public by Us on the Karma Platform. 
	\item The transaction comment is public by default, but can be recorded privately, therefore making only the recipient, expediter and amount public.
\end{enumerate}

\section{Claiming Karma}

\begin{enumerate}
	\item 
\end{enumerate}

\section{Warranties and Disclaimers}

We provide our Services using a reasonable level of skill and care an we hope that you enjoy using them, but there are certain things that we don't promise about our Services.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.

\end{document}