\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\lfoot{v. 2017-02-09}
\cfoot{Page \thepage}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}

\setlength\parindent{0pt}

\author{Ilya Skurikhin}
\title{Karma Terms of Service}



\begin{document}

\begin{center}
{\Huge Karma \\ \vspace{5mm} Terms of Service} \\
\end{center}

\vspace{5mm}

We thank you for using the Karma Platform. By using these products and services ("Services"), you are agreeing to these terms. Please read them carefully.

\section{Definitions}

\paragraph{Language}

This agreement was written in English (US). To the extent any translated version of this agreement conflicts with the English version, the English version controls.

\paragraph{Residence}

The living community ("colocation") situated at 75, Rue de Genève, 1004 Lausanne, Switzerland.

\paragraph{Resident}

A person who is living in the Residence, and who's lease is substantiated by a current and valid lease agreement ("bail à loyer").

\paragraph{We}

("us", "our") are the developers of the Karma Platform. 

\paragraph{You}

("your") are the user of the Karma Platform ("KP"); delegates will be considered users if authorized by a Resident.
	
\paragraph{Karma}

are points that can be received and transferred by You. The official abbreviation of the Karma is "K".

\paragraph{Karma Platform}

is the web interface through which users may make transfers of points and consult their balance. 

\section{Privacy}

Your privacy is very important to us. \\

We collect information to provide better Services to our users. \\

We will share information with companies, organizations or individuals outside of KP if we have a good-faith belief that access, use, preservation or disclosure of the information is necessary to: meet a law, regulation, or enforceable government request; enforce the Terms of Service, including investigation of potential violations; detect, address, or prevent fraud, security or other technical issues. \\

We may share non-personally identifiable information publicly. For example, we may share information publicly to show tendencies in the flow of Karma. 

\section{Using our Services}

Don't misuse our Services. \\

Please follow the terms and use Services in the way that as we describe them in the interface and instructions we provide. You may use our Services only as permitted by law. We may stop providing our Services to you if you do not comply with our terms, or if we are suspecting misconduct.\\

Using our Services does not give you ownership of any of the intellectual property rights in our Services or the content you access. You may not use content from our Services unless you obtain prior permission from its owner. \\

In connection with your use of our Services, we may send you service announcements, administrative messages, and other information. \\

Some of our Services are available on mobile devices. Do not use these Services in a way that will divert your attention while driving, or prevents you from obeying traffic laws.

\section{Your Account}

In order to use the Karma Platform, You will need an account. An account will be assigned to you by an administrator when you move in to the Residence. \\

To protect Your account, keep your password confidential. You are responsible for the activity that happens on or through Your account.

\section{Changes}

We may change and improve our services. We may add functionalities or features, and we may suspend or stop Services. \\

We may modify these terms or any additional terms that apply to a Service. You should look at these terms regularly. Changes will not apply retroactively. If you do not agree to the modified terms for the Services, you should discontinue your use of the Services.


\section{Warranties and Disclaimers}

We provide our Services using a reasonable level of skill and care an we hope that you enjoy using them, but there are certain things that we don't promise about our Services. \\

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT, TO THE EXTENT PERMITTED BY LAW.

IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM,  DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.

WE WILL NOT BE LIABLE FOR ANY LOSS, WHETHER DATA, FINANCIAL OR SOCIAL.

\end{document}